### 2024-01-29 tesis_Ashish/Abstract/abstract.tex
Updated thesis 4 Jan 2024
update
29 Jan update

The Pixel Cluster Counting (PCC) luminosity measurement method has emerged as a reliable offline technique for luminosity measurement developed for the CMS experiment.
%The PCC method is based on the rate of pixel clusters in the CMS pixel detector, which is the innermost part of the CMS tracker.
The PCC method is studied for its precision in luminosity measurement using 2017, 2018 and 2022  datasets. The results of these studies demonstrate that the PCC luminosity measurement method is stable and linear, able to achieve final uncertainty on the luminosity measurement at the level of 1\% or better.  Final systematic uncertainty achieved on luminosity measurement for 2018 and 2022 datasets are 1.08\% and 1.5\% respectively. %1\% systematic uncertainty on the final luminosity measurement.
Moreover, the clusters and coincidences counting algorithms and their optimization for the Phase II High Luminosity LHC (HL-LHC) luminosity measurement are also developed, using simulated datasets for the proposed Phase II pixel detector. %This new pixel detector will replace the Run 2 pixel detector.
Linearity of the Tracker endcap pixel (TEPX) and Disk 4 Ring 1 luminometers are expected to be within 1\% (offline) up to a pileup of 200 and their statistical precision per second is about 0.1\% at pileup 200.
%It is expected to provide excellent statistical precision and linearity performance, which is essential for precision luminosity measurements at the HL-LHC.

>>>>

The Pixel Cluster Counting (PCC) luminosity measurement method has emerged as a reliable offline technique for luminosity measurement developed for the CMS experiment.
%The PCC method is based on the rate of pixel clusters in the CMS pixel detector, which is the innermost part of the CMS tracker.
The PCC method is studied for its precision in luminosity measurement using 2017, 2018 and 2022  datasets. The results of these studies demonstrate that the PCC luminosity measurement method is stable and linear. %able to achieve final uncertainty on the luminosity measurement at the level of 1\% or better.
Final systematic uncertainty achieved on luminosity measurement for 2018 and 2022 datasets are 2.2\% and
is 1.5\% respectively. %1\% systematic uncertainty on the final luminosity measurement.
Moreover, the clusters and coincidences counting algorithms and their optimization for the Phase II High Luminosity LHC (HL-LHC) luminosity measurement are also developed, using simulated datasets for the proposed Phase II pixel detector. %This new pixel detector will replace the Run 2 pixel detector.
Linearity of the Tracker endcap pixel (TEPX) and Disk 4 Ring 1 luminometers are expected to be within 1\% (offline) up to a pileup of 200 and their statistical precision per second is about 0.1\% at pileup 200.
%It is expected to provide excellent statistical precision and linearity performance, which is essential for precision luminosity measurements at the HL-LHC.

### 2024-01-29 tesis_Ashish/Chapter5/chapter5.tex
29 Jan update

Type-2 parameters, derived from a preceding study using Random trigger data, are presumed to remain constant during the year. The fitting template is given by:
\begin{equation}
F(x) = \Sigma_{k=0}^{N_{bcid}} N_k \left[(x-k==0)+\alpha\cdot(x-k==1)+A \cdot e^{-\tau\cdot(x-k-1)}(x-k>=1) \right]
\end{equation}
with $k$ denoting the colliding bunch crossing and $x$ indicating the histogram bin. 2022 PCC afterglow model uses run number 361957 for doing fit to type 1 and type 2 afterglow effect in the PCC raw data as shown in Fig. \ref{fig:period_bound_101}. Model consist of a parameter for type 1 afterglow correcton and exponentially decaying function with two parameters amplitude and decay width to model type 2 afterglow correction. Fit function is summed over all bunch crossings. Fit perfomed for 4 wagon train is shown in Fig.  \ref{fig:period_bound_102} in run 361957 to compute type 2 afterglow amplitude and decay width. The values obtained for type 2 afterglow amplitude and decay parameters are 0.0007915 and 0.00918 respectively \cite{pas_22}. %\cite{bril2023afterglow}.
%as shown in Table. \ref{table:trains_data}.

@@

\newpage
Table \ref{table:correction_uncertainties} provides a detailed breakdown of the systematic uncertainties associated with the luminosity measurement for the year 2022. Each row represents a specific correction factor, while the corresponding column indicates its associated uncertainty as a percentage.

\begin{table}[H]
  \centering
  \caption{Systematic uncertainty in luminosity measurement (\%)}
    \begin{tabular}{l|c}
        \textbf{Source} & \textbf{Uncertainty (\%)} \\
        \hline
        \multicolumn{2}{c}{\textbf{Calibration}} \\
        \hline
        Beam current & 0.3 \\
        Orbit drift & 0.3 \\
        Residual beam positions & 0.4 \\
        Beam-beam effects & 0.4 \\
        Length scale & 0.1 \\
        Factorization bias & 0.8 \\
        Scan-to-scan variation & 0.5 \\
        Bunch-to-bunch variation & 0.1 \\
        Cross-detector consistency & 0.4 \\
        \hline
        \multicolumn{2}{c}{\textbf{Integration}} \\
        \hline
        Afterglow corrections & 0.2 \\
        Cross-detector stability & 0.5 \\
        Cross-detector linearity & 0.5 \\
        \hline
        Calibration & 1.3 \\
        Integration & 0.8 \\
        \hline
        \textbf{Total} & 1.4 \\
    \end{tabular}
    \label{table:correction_uncertainties}
    %\caption{Systematic uncertainty in luminosity measurement (\%)}
\end{table}

>>>>

Type-2 parameters, derived from a preceding study using Random trigger data, are presumed to remain constant during the year. The fitting template is given by:
\begin{equation}
F(x) = \Sigma_{k=0}^{N_{bcid}} N_k \left[(x-k==0)+\alpha\cdot(x-k==1)+A \cdot e^{-\tau\cdot(x-k-1)}(x-k>=1) \right]
\end{equation}
with $k$ denoting the colliding bunch crossing and $x$ indicating the histogram bin. 2022 PCC afterglow model uses run number 361957 for doing fit to type 1 and type 2 afterglow effect in the PCC raw data as shown in Fig. \ref{fig:period_bound_101}. Model consist of a parameter for type 1 afterglow correcton and exponentially decaying function with two parameters amplitude and decay width to model type 2 afterglow correction. Fit function is summed over all bunch crossings. Fit perfomed for 4 wagon train is shown in Fig.  \ref{fig:period_bound_102} in run 361957 to compute type 2 afterglow amplitude and decay width. The values obtained for type 2 afterglow amplitude and decay parameters are 0.0008406 and 0.01047 respectively \cite{pas_22}. %\cite{bril2023afterglow}.
%as shown in Table. \ref{table:trains_data}.

@@

Table \ref{table:correction_uncertainties} provides a detailed breakdown of the systematic uncertainties associated with the luminosity measurement for the year 2022. Each row represents a specific correction factor, while the corresponding column indicates its associated uncertainty as a percentage.

\begin{table}[H]
  \centering
  \caption{Systematic uncertainty in luminosity measurement (\%) \cite{pas_22}}
    \begin{tabular}{l|c}
        \textbf{Source} & \textbf{Uncertainty (\%)} \\
        \hline
        \multicolumn{2}{c}{\textbf{Calibration}} \\
        \hline
        Beam current & 0.3 \\
        Orbit drift & 0.3 \\
        Residual beam positions & 0.4 \\
        Beam-beam effects & 0.4 \\
        Length scale & 0.1 \\
        Factorization bias & 0.8 \\
        Scan-to-scan variation & 0.5 \\
        Bunch-to-bunch variation & 0.1 \\
        Cross-detector consistency & 0.4 \\
        \hline
        \multicolumn{2}{c}{\textbf{Integration}} \\
        \hline
        Afterglow corrections & 0.2 \\
        Cross-detector stability & 0.5 \\
        Cross-detector linearity & 0.5 \\
        \hline
        Calibration & 1.3 \\
        Integration & 0.8 \\
        \hline
        \textbf{Total} & 1.5 \\
    \end{tabular}
    \label{table:correction_uncertainties}
    %\caption{Systematic uncertainty in luminosity measurement (\%)}
\end{table}

### 2024-01-29 tesis_Ashish/Chapter8/chapter8.tex
update 27 Jan
29 Jan update

In Chapter 4, the results from Run 2 (2017 and 2018) are comprehensively detailed. %For the year 2018, the integrated luminosity was calculated to be \(60.47 \, \text{fb}^{-1}\).
The visible cross section was accurately determined as \(960.54 \pm 0.85 \, (\text{stat.}) \, \text{mb}\). A total of 155 good pixel modules were selected for the final luminosity measurement. Systematic uncertainties were meticulously quantified, including scan to scan (\(0.3\%\)), bunch to bunch (\(0.1\%\)), afterglow (\(0.3\%\)), linearity (\(0.4\%\)), and cross detector stability (\(0.3\%\)). Work is ongoing to complete this measurement. The total uncertainty is expected to be order of 1\%.

In Chapter 5, significant results from the PCC luminosity measurement during Run 3 (2022) are outlined. %The chapter reports that the PCC integrated luminosity for 2022 was computed to be \(38.61 \, \text{fb}^{-1}\) .
Furthermore, a comprehensive analysis of systematic uncertainties in the luminosity measurement for the year 2022 is presented. These uncertainties encompass a range of factors including calibration (1.2\%), integration (0.8\%), and other specific sources such as beam current (0.3\%), orbit drift (0.3\%), and cross-detector linearity (0.5\%), culminating in a total uncertainty of \(1.4\%\).

>>>>

In Chapter 4, the results from Run 2 (2017 and 2018) are comprehensively detailed. %For the year 2018, the integrated luminosity was calculated to be \(60.47 \, \text{fb}^{-1}\).
The visible cross section was accurately determined as \(960.54 \pm 0.85 \, (\text{stat.}) \, \text{mb}\). A total of 155 good pixel modules were selected for the final luminosity measurement. %Systematic uncertainties were meticulously quantified, including scan to scan (\(0.3\%\)), bunch to bunch (\(0.1\%\)), afterglow (\(0.3\%\)), linearity (\(0.4\%\)), and cross detector stability (\(0.3\%\)). Work is ongoing to complete this measurement.
The total systematic uncertainty is expected to be order of 2.2\% which is better than LUM PAS 18 results. Work is ongoing to complete this measurement and we expect significant improvement in beam-beam systematic uncertainties.

In Chapter 5, results from the PCC luminosity measurement during Run 3 (2022) are outlined. %The chapter reports that the PCC integrated luminosity for 2022 was computed to be \(38.61 \, \text{fb}^{-1}\) .
Furthermore, a comprehensive analysis of systematic uncertainties in the luminosity measurement for the year 2022 is presented. %These uncertainties encompass a range of factors including calibration (1.2\%), integration (0.8\%), and other specific sources such as beam current (0.3\%), orbit drift (0.3\%), and cross-detector linearity (0.5\%)
Total systematic uncertainty is \(1.5\%\).

### 2024-01-29 tesis_Ashish/Dedication/dedication.tex
Updated thesis 14 Jan 2024
29 Jan update

\begin{dedication}
\begin{center}
    \section*{Acknowledgement}
\end{center}
\justify{

@@

I am indebted to my friends and colleagues, especially Rohit Gupta and Mohammad Balal, for their valuable insights, stimulating discussions, and enduring support. Their encouragement, camaraderie,and intellectual exchanges have been instrumental in shaping both my research and personal growth.

>>>>

\begin{dedication}
  \vspace*{-2cm} % Adjust the -2cm to the amount of space you want to move up
%\centering
%\begin{center}
\section*{Acknowledgement}
%\end{center}
\justify{

@@

I am indebted to my friends and colleagues, especially Rohit Gupta and Mohammad Balal, for their valuable insights, stimulating discussions, and enduring support. Their encouragement, camaraderie and intellectual exchanges have been instrumental in shaping both my research and personal growth.

### 2024-01-29 tesis_Ashish/Portada/Portada.tex
29 Jan update

 %% Aquí comienza el documento.
\thispagestyle{empty} %% PARA QUITAR FORMATO DE PIES Y ENCABEZADOS DE PÁGINA A LA PORTADA
%
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%% MINIPAGE PARA EL LOGO DEL LADO IZQUIERDO (UNIVERSIDAD) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%\fbox{
\begin{minipage}[c][0.15\textheight][c]{0.25\textwidth}
    \begin{center}
        \includegraphics[height=3.2cm, keepaspectratio=true]{unison-logo.png} %% LOGO IZQUIERDO
    \end{center}
\end{minipage}
%}
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%%%%%% MINIPAGE PARA EL CUERPO DE LA PORTADA (NOMBRES, TITULOS, ETC.) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%
%
%
%
%\fbox{
\begin{minipage}[c][0.17\textheight][t]{0.7\textwidth}
    \begin{center}
        {\scshape\LARGE UNIVERSIDAD DE SONORA} %% NOMBRE DE LA UNIVERSIDAD
        \vspace{.5cm}   %% DEFINE EL ESPACIO ENTRE EL NOMBRE DE LA UNIVERSIDAD Y LA LÍNEA DOBLE
        \hrule height2.5pt  %% DEFINE EL ANCHO DE LA PRIMER LÍNEA
        \vspace{.1cm}    %% DEFINE EL ESPACIO ENTRE LAS DOS LINEAS
        \hrule height1pt  %% DEFINE EL ANCHO DE LA SEGUNDA LINEA (NORMALMENTE ES MAS DELGADA)
        \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
        {\scshape \large Divisi\'on de Ciencias Exactas y Naturales}
        {\scshape Departamento de Investigaci\'on en F\'isica} %% NOMBRE DE LA DIVISIÓN
    \end{center}
\end{minipage}
%}
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%% MINIPAGE PARA EL LOGO DEL LADO DERECHO (DIVISIÓN ACADÉMICA)
%
%
%
%
%\fbox{

>>>>

 %% Aquí comienza el documento.
\thispagestyle{empty} %% PARA QUITAR FORMATO DE PIES Y ENCABEZADOS DE PÁGINA A LA PORTADA
%
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%% MINIPAGE PARA EL LOGO DEL LADO IZQUIERDO (UNIVERSIDAD) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%\fbox{
\begin{minipage}[c][0.15\textheight][c]{0.25\textwidth}
    \begin{center}
        \includegraphics[height=3.2cm, keepaspectratio=true]{unison-logo.png} %% LOGO IZQUIERDO
    \end{center}
\end{minipage}
%}
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%%%%%% MINIPAGE PARA EL CUERPO DE LA PORTADA (NOMBRES, TITULOS, ETC.) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%
%
%
%
%\fbox{
\begin{minipage}[c][0.17\textheight][t]{0.7\textwidth}
    \begin{center}
        {\scshape\LARGE UNIVERSIDAD DE SONORA} %% NOMBRE DE LA UNIVERSIDAD
        \vspace{.5cm}   %% DEFINE EL ESPACIO ENTRE EL NOMBRE DE LA UNIVERSIDAD Y LA LÍNEA DOBLE
        \hrule height2.5pt  %% DEFINE EL ANCHO DE LA PRIMER LÍNEA
        \vspace{.1cm}    %% DEFINE EL ESPACIO ENTRE LAS DOS LINEAS
        \hrule height1pt  %% DEFINE EL ANCHO DE LA SEGUNDA LINEA (NORMALMENTE ES MAS DELGADA)
        \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
        %{\scshape \large Divisi\'on de Ciencias Exactas y Naturales}
        {\scshape Departamento de Investigaci\'on en F\'isica} %% NOMBRE DE LA DIVISIÓN
    \end{center}
\end{minipage}
%}
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%% MINIPAGE PARA EL LOGO DEL LADO DERECHO (DIVISIÓN ACADÉMICA)
%
%
%
%
%\fbox{
